Report and Figures

### 2016-10-06 tex/paper/methods.tex

		\item[Organizational Equivalence:] Both the theoretical definition \eqref{eq:def_J} and the procedure to compute it from tract data remain unchanged when a tract is subdivided into smaller tracts, each of which with identical demographic structure. 
		\item[Size and Density Invariance:] Since $J(X,Y)$ is completely determined by the marginal distribution $p(X,Y)$, it is invariant under changes in population density. 
		\item[Additive Group Decomposability:] When demographic groups are aggregated into super-groups, the chain rule of mutual information applied to the demographic variable $Y$ provides an an additive decomposition of the form $J(X,Y) = J(X,G) + J(X,Y|G)$, which can be interpreted as the sum of a between-groups term and a within-groups term as needed.
		\item[Scale Interpretability:] We have $J(X,Y) = 0$ if and only if $p(Y|X)$ is constant on each connected component of the metric space $M$. When only one connected component exists, this implies that every locale has the same demographic structure as the global environment. When multiple connected components exist (e.g. the city is divided by a river), demographics must be constant in space on each side of the division. $J(X,Y)$ does not satisfy the additional condition of achieving its maximum value when all locales are monoracial, but this point only emphasizes that $J(X,Y)$ and $I(X,Y)$ should be read jointly. When all locales are monoracial, $I(X,Y)$ achieves its maximum value and $J(X,Y) = 0$. 
		\item[Boundary Independence:] $J(X,Y)$ is defined in terms of a continuous underlying probability distribution $p(X,Y)$, rather than arbitrarily-defined tracts. In computational practice, $J(X,Y)$ is indeed sensitive to the boundaries supplied with the data; however, \eqref{eq:approx} guarantees that this sensitivity vanishes as the resolution grows sufficiently small. No alternative measure can overcome limited data resolution, and, to our knowledge, no other measure comes with the same assurance of resolution-independence in the limit. 
		\item[Transfers and Exchanges:] The core idea of the principles of transfers and exchanges is that population permutations that tend to ``smooth out'' differences should reduce segregation measures. However, the concrete principles as stated in \cite{Reardon2002} do not hold of $J(X,Y)$. The core point is that $J(X,Y)$ compares distributions to those nearby, so whether or not a transfer or exchange reduces $J(X,Y)$depends not only on the two regions involved in the transfer or exchange, but also the regions surrounding them. $I(X,Y)$ does satisfy the two principles. % Consider trying to demonstrate the spatial transfer principle for the computational version. 

@@

	We close with a discussion of some of the theoretical and operational virtues of $I(X,Y)$ and $J(X,Y)$ not considered above. 
	\begin{description}
		\item[Interpretability:] In contrast to many previous works, we make no attempt to encapsulate every aspect of diversity in a single measure. The result of maintaining distinct measures is that each of our two separate measures are highly interpretable. The mutual information $I(X,Y)$has a standard interpretation in information theory: it is the epistemic value of knowing where an individual lives for the purposes of predicting their race, as measured using the logarithmic loss function; see \cite{Cover1991} for a detailed discussion of information measures and prediction. The local information $J(X,Y)$ is then interpretable as the epistemic value of knowing where an individual lives when restricting one's attention to a small area. The direct operational meaning of these metrics is the source of their desirable mathematical properties, and reflects the virtue of starting from a unified mathematical framework.  
		\item[Kernel Independence:] Many existing spatial information measures depend on a choice of spatial kernel function which serves as a functional definition of proximity. While providing flexibility, dependence on a spatial kernel function increases researcher degrees of freedom and makes it more difficult to compare studies. There is no theoretical consensus on the appropriate kernel. The mutual information $I(X,Y)$ is aspatial and requires no kernel. In practice, computing $J(X,Y)$ does require a choice of a grid radius (see Appendix for details), but does not require the specification of a functional kernel. 
		\item[Isotropy:] As a result of its kernel independence, $J(X,Y)$ is \emph{isotropic}, taking no consideration of natural boundaries or infrastructure. This property has both virtues and drawbacks. On the one hand, an isotropic measure is simple to compute, simple to interpret, and easily generalized. On the other, boundaries and infrastructure unquestionable shape interactions between people, and are clearly relevant in segregation studies. We note, however, that most urban anisotropies exist on the scale of a few hundred meters at most. Therefore, we expect that anisotropic measures will only be relevant at scales of analysis substantially smaller than the 500m used in this study. A detailed numerical comparison of isotropic and anisotropic measures would be most welcome. 
		\item[Connection to Data Analysis:] As we will see below, the mutual information $I(X,Y)$ can be used to define a practical algorithm for the identification of natural, demographically coherent neighborhoods, and the local information $J(X,Y)$ predicts its performance. These two measures are thus not only of theoretical interest, but also provide tools for the practical analysis of urban diversity. We are not aware of any other measures that share this helpful property. 
	\end{description}

>>>>

		\item[Organizational Equivalence:] Both the theoretical definition \eqref{eq:def_J} and the procedure to compute it from discrete data remain unchanged when a tract is subdivided into smaller tracts, each of which with identical demographic structure. 
		\item[Size and Density Invariance:] Since $J(X,Y)$ is completely determined by the probability measure $p(X,Y)$, it is invariant under global changes in population density. 
		\item[Additive Group Decomposability:] When demographic groups are aggregated into super-groups, the chain rule of mutual information applied to the demographic variable $Y$ provides an an additive decomposition of the form $J(X,Y) = J(X,G) + J(X,Y|G)$ for the mean local information. This can be interpreted as a sum of between-groups and within-gropus terms as required. 
		\item[Scale Interpretability:] We have $J(X,Y) = 0$ if and only if $p(Y|X)$ is constant on each connected component of the metric space $M$. When only one connected component exists, this implies that every locale has the same demographic structure as the global environment. When multiple connected components exist (e.g. the city is divided by a river), demographics must be constant in space on each side of the division. $J(X,Y)$ does not achieve its maximum value when all locales are monoracial, but this point only emphasizes that $J(X,Y)$ and $I(X,Y)$ should be read jointly. When all locales are monoracial, $I(X,Y)$ achieves its maximum value and $J(X,Y) = 0$. 
		\item[Boundary Independence:] $J(X,Y)$ is defined in terms of a continuous underlying probability distribution $p(X,Y)$, rather than arbitrarily-defined tracts. In computational practice, $J(X,Y)$ is indeed sensitive to the boundaries supplied with the data; however, \eqref{eq:approx} guarantees that this sensitivity vanishes as the resolution grows sufficiently small. No alternative measure can overcome limited data resolution, and, to our knowledge, no other measure comes with the same assurance of limiting resolution independence. 
		\item[Transfers and Exchanges:] The core idea of the principles of transfers and exchanges is that population permutations that tend to ``smooth out'' differences should reduce segregation measures. No strict such condition holds for $J(X,Y)$; however, this is comparatively not a large limitation, as most of the measures considered in \cite{Reardon2004} also fail to meet rigorous transfer and exchange principles. $J(X,Y)$ does satisfy the following useful and interpretable criterion: when a transfer makes all affected areas more closely resemble their immediate neighbors, $J(X,Y)$ decreases. Notably, these transfers can tend to either increase or reduce spatial evenness, and $I(X,Y)$ may increase or decrease accordingly. 

@@

	We close with a discussion of some of the theoretical and operational virtues of $I(X,Y)$ and $J(X,Y)$ not considered above. 
	\begin{description}
		\item[Interpretability:] In contrast to many previous works, we make no attempt to encapsulate every aspect of diversity in a single measure. The result of maintaining distinct measures is that each of our two separate measures are highly interpretable. The mutual information $I(X,Y)$has a standard interpretation in information theory: it is the epistemic value of knowing where an individual lives for the purposes of predicting their race, as measured using the logarithmic loss function; see \cite{Cover1991} for a detailed discussion of information measures and prediction. The local information $J(X,Y)$ is then interpretable as the epistemic value of knowing where an individual lives when restricting one's attention to a small area. The direct operational meaning of these metrics is the source of their desirable mathematical properties, and reflects the virtue of starting from a unified mathematical framework.  
		\item[Kernel Independence:] Many existing spatial information measures depend on a choice of spatial kernel function which serves as a functional definition of proximity. While providing flexibility, dependence on a spatial kernel function increases researcher degrees of freedom and makes it more difficult to compare studies. There is no theoretical consensus on the appropriate kernel. The mutual information $I(X,Y)$ is aspatial and requires no kernel. In practice, computing $J(X,Y)$ does require a choice of a grid radius (see Appendix for details), but does not require the specification of a functional kernel. 
		\item[Isotropy:] As a result of its kernel independence, $J(X,Y)$ is \emph{isotropic}, taking no consideration of natural boundaries or infrastructure. This property has both virtues and drawbacks. On the one hand, an isotropic measure is simple to compute, simple to interpret, and easily generalized. On the other, boundaries and infrastructure unquestionably shape interactions between people, and are clearly relevant in segregation studies. We note, however, that most urban anisotropies exist on the scale of a few hundred meters at most. Therefore, we expect that anisotropic measures will only be relevant at scales of analysis substantially smaller than the 500m used in this study. A detailed numerical comparison of isotropic and anisotropic measures would be most welcome. 
		\item[Connection to Data Analysis:] As we will see below, the mutual information $I(X,Y)$ can be used to define a practical algorithm for the identification of natural, demographically coherent neighborhoods, and the local information $J(X,Y)$ predicts its performance. These two measures are thus not only of theoretical interest, but also provide tools for the practical analysis of urban diversity. We are not aware of any other measures that share this helpful property. 
	\end{description}

	\begin{figure}
		\begin{tabular}{l | c c c}
		Criterion & $H(Y)$ & $I(X,Y)$ & $J(X,Y)$ \\
		\hline
		Scale Interpretability & \checkmark & \checkmark & \checkmark \\
		Density Invariance & & & \\
		Compositional Invariance & & & \\
		Transfers & & & \\
		Additive Organizational Decomposability & & & \\
		Additive Spatial Decomposability & & & 
		\end{tabular}
	\end{figure}
